Dataset of operator-client dialogues aligned with database queries

### 2016-06-28 paper.tex
fit 9 pages included references
submitted version - todo preprint oplatek sds
change title

\title{Dataset of operator-client dialogues aligned with knowledge-base queries}

@@

\begin{abstract}
    This paper presents a novel dataset for training end-to-end task oriented conversational agents.
    The dataset contains task oriented conversations between an operator – a task expert, and a client who is seeking information about the task, along with records of database API calls performed by the operator, which capture the distilled meaning of the user query.
    We expect that thanks to this easy-to-get supervision of database calls one would require significantly less training data for training end-to-end dialogue agents.
 	The dataset is collected using crowdsourcing on well known restaurant domain.
    The quality of the data is enforced by mutual control among contributors and manually verified on random sub-sample.
    The dataset is available for download under the Creative Commons 4.0 BY-SA license.
\end{abstract}

@@

\vspace{-1.00em}
\subsubsection*{Acknowledgments}
We would like to thank Ondřej Dušek for useful comments.
This research was partly funded by the Ministry of Education, Youth and Sports of the Czech Republic under the grant agreement LK11221, core research funding, grant GAUK 1915/2015, and also partially supported by SVV project number 260 333. 
% We gratefully acknowledge the support of NVIDIA Corporation with the donation of the Tesla K40c GPU used for this research.
% Cloud computational resources were provided by the MetaCentrum under the program LM2010005 and the CERIT-SC under the program Center CERIT Scientific Cloud, part of the Operational Program Research and Development for Innovations, Reg.\ no. CZ.1.05/3.2.00/08.0144.

@@

% Winery~\cite{Winery} is graphical \commentontext{modeling}{modeling with one \enquote{l}, because of AE} tool.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-1.00em}
\bibliographystyle{splncs03}
\bibliography{paper}
\vspace{-1.00em}

>>>>

\title{Dataset of operator-client dialogues aligned with database queries}

@@

\begin{abstract}
    This paper presents a novel dataset for training end-to-end task oriented conversational agents.
    The dataset contains task oriented conversations between an operator – a task expert, and a client who is seeking information about the task, along with records of database API calls performed by the operator, which capture the distilled meaning of the user query.
    We expect that thanks to this easy-to-get supervision of database calls one would require significantly less training data for training end-to-end dialogue agents.
 	The dataset is collected using crowdsourcing on well known restaurant domain.
    The quality of the data is enforced by mutual control among contributors.  % TODO and manually verified on random sub-sample 
    The dataset is available for download under the Creative Commons 4.0 BY-SA license.
\end{abstract}

@@

\vspace{-1.40em}
\subsubsection*{Acknowledgments}
We would like to thank Ondřej Dušek for useful comments.
This research was partly funded by the Ministry of Education, Youth and Sports of the Czech Republic under the grant agreement LK11221, core research funding, grant GAUK 1915/2015, and also partially supported by SVV project number 260 333. 
% We gratefully acknowledge the support of NVIDIA Corporation with the donation of the Tesla K40c GPU used for this research.
% Cloud computational resources were provided by the MetaCentrum under the program LM2010005 and the CERIT-SC under the program Center CERIT Scientific Cloud, part of the Operational Program Research and Development for Innovations, Reg.\ no. CZ.1.05/3.2.00/08.0144.

@@

% Winery~\cite{Winery} is graphical \commentontext{modeling}{modeling with one \enquote{l}, because of AE} tool.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-1.00em}
\bibliographystyle{splncs03}
\bibliography{paper}
